---
title: "ryx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ryx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ryx)
```

# ryx
The ryx package intends to make calculating and visualizing correlations easier.

## print.ryx
The print function prints out an object displaying the correlation, the p-values and the significance of the p-values of all the selected outcome variables against the response variable.
```{r}
data(mtcars)
print(ryx(mtcars, y = "mpg", x = c("hp", "wt", "disp", "cyl", "am", "gear")))
```


## summary.ryx
The summary function summarized in only a few sentences what variables your a correlating with your response variable. It displays the median, the range, the amount of statistically significant correlations, and all the variables involved the variables used.
```{r}
summary(ryx(mtcars, y = "mpg", x = c("hp", "wt", "disp", "cyl", "am", "gear")))
```


## plot.ryx
The plot function displays the correlation of all the outcome variables against the response variable.
```{r}
plot(ryx(mtcars, y = "mpg", x = c("hp", "wt", "disp", "cyl", "am", "gear")))
```

